---
title: "Check clean data"
output: html_notebook
---

This script checks the clean datasets. 

```{r, include= FALSE}
library(here)
library(tidyverse)
```


# 1. Le Monde

```{r}
dat <- here("data","clean_newspapers","lemonde.rds") %>% read_rds()
dat %>% glimpse
dat %>% skimr::skim()
```

```{r}
dat %>% 
  filter(date > "1985-01-01") %>% 
  mutate(date = lubridate::as_date(date)) %>% 
  ggplot(aes(date)) + geom_histogram(binwidth = 7) + 
  theme_bw() 
```

Share of articles with "europ*" or "brexit" in the title
```{r}
dat %>% 
  filter(date > "1985-01-01") %>% 
  mutate(date = lubridate::as_date(date), 
         month = date %>% lubridate::floor_date(unit = "months"), 
         europ_title = str_detect(str_to_lower(title), "europ|brexit")) %>% 
  group_by(month) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(month, europ_title)) + geom_col() + 
  theme_bw() + 
  labs(x="month",y="Share of articles with europ/brexit in title")
```

# 2. Le Figaro

```{r}
dat <- here("data","clean_newspapers","figaro.rds") %>% read_rds()
dat %>% glimpse
dat %>% skimr::skim()
```

```{r}
dat %>% 
  mutate(date = lubridate::as_date(date)) %>% 
  ggplot(aes(date)) + geom_histogram(binwidth = 7) + 
  theme_bw() 
```

Share of articles with "europ*" or "brexit" in the title
```{r}
dat %>% 
  mutate(date = lubridate::as_date(date), 
         month = date %>% lubridate::floor_date(unit = "months"), 
         europ_title = str_detect(str_to_lower(title), "europ|brexit")) %>% 
  group_by(month) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(month, europ_title)) + geom_col() + 
  theme_bw() + 
  labs(x="month",y="Share of articles with europ/brexit in title")
```

# 3. La Repubblica

```{r}
dat <- here("data","clean_newspapers","repubblica.rds") %>% read_rds()
dat %>% glimpse
dat %>% skimr::skim()
```

```{r}
dat %>% 
  mutate(date = lubridate::as_date(date)) %>% 
  ggplot(aes(date)) + geom_histogram(binwidth = 7) + 
  theme_bw() 
```

Share of articles with "europ*" or "brexit" in the title
```{r}
dat %>% 
  mutate(date = lubridate::as_date(date), 
         month = date %>% lubridate::floor_date(unit = "months"), 
         europ_title = str_detect(str_to_lower(title), "europ|brexit")) %>% 
  group_by(month) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(month, europ_title)) + geom_col() + 
  theme_bw() + 
  labs(x="month",y="Share of articles with europ/brexit in title")
```


# 4. Le Corriere della Sera

```{r}
dat <- here("data","clean_newspapers","corriere.rds") %>% read_rds()
dat %>% glimpse
dat %>% skimr::skim()
```

```{r}
dat %>% 
  mutate(date = lubridate::as_date(date)) %>% 
  ggplot(aes(date)) + geom_histogram(binwidth = 7) + 
  theme_bw() 
```

Share of articles with "europ*" or "brexit" in the title
```{r}
dat %>% 
  mutate(date = lubridate::as_date(date), 
         month = date %>% lubridate::floor_date(unit = "months"), 
         europ_title = str_detect(str_to_lower(title), "europ|brexit")) %>% 
  group_by(month) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(month, europ_title)) + geom_col() + 
  theme_bw() + 
  labs(x="month",y="Share of articles with europ/brexit in title")
```

# 5. El Mundo

```{r}
dat <- here("data","clean_newspapers","elmundo.rds") %>% read_rds()
dat %>% glimpse
dat %>% skimr::skim()
```

```{r}
dat %>% 
  filter(date > "1900-01-01") %>% 
  mutate(date = lubridate::as_date(date)) %>% 
  ggplot(aes(date)) + geom_histogram(binwidth = 7) + 
  theme_bw() 
```

Share of articles with "europ*" or "brexit" in the title
```{r}
dat %>% 
  filter(date > "1900-01-01") %>% 
  mutate(date = lubridate::as_date(date), 
         month = date %>% lubridate::floor_date(unit = "months"), 
         europ_title = str_detect(str_to_lower(title), "europ|brexit")) %>% 
  group_by(month) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(month, europ_title)) + geom_col() + 
  theme_bw() + 
  labs(x="month",y="Share of articles with europ/brexit in title")
```

# 6. El Pais

```{r}
dat <- here("data","clean_newspapers","elpais.rds") %>% read_rds()
dat %>% glimpse
dat %>% skimr::skim()
```

```{r}
dat %>% 
  mutate(date = lubridate::as_date(date)) %>% 
  ggplot(aes(date)) + geom_histogram(binwidth = 7) + 
  theme_bw() 
```

Share of articles with "europ*" or "brexit" in the title
```{r}
dat %>% 
  mutate(date = lubridate::as_date(date), 
         month = date %>% lubridate::floor_date(unit = "months"), 
         europ_title = str_detect(str_to_lower(title), "europ|brexit")) %>% 
  group_by(month) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(month, europ_title)) + geom_col() + 
  theme_bw() + 
  labs(x="month",y="Share of articles with europ/brexit in title")
```


# 7. Publico

```{r}
dat <- here("data","clean_newspapers","publico.rds") %>% read_rds()
dat %>% glimpse
dat %>% skimr::skim()
```

```{r}
dat %>% 
  mutate(date = lubridate::as_date(date)) %>% 
  ggplot(aes(date)) + geom_histogram(binwidth = 7) + 
  theme_bw() 
```

Share of articles with "europ*" or "brexit" in the title
```{r}
dat %>% 
  mutate(date = lubridate::as_date(date), 
         month = date %>% lubridate::floor_date(unit = "months"), 
         europ_title = str_detect(str_to_lower(title), "europ|brexit")) %>% 
  group_by(month) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(month, europ_title)) + geom_col() + 
  theme_bw() + 
  labs(x="month",y="Share of articles with europ/brexit in title")
```


