---
title: "Summary stats"
output: html_notebook
---

This script checks the clean datasets. 

```{r, include= FALSE}
library(here)
library(tidyverse)
```


```{r}
allnews <- here::here("data","clean_newspapers","all_newspapers.rds") %>% read_rds()
```


# 1. Length of articles

```{r}
allnews %>% 
  mutate(size_body = nchar(body), 
         yearmonth = date %>% lubridate::floor_date(unit="months")) %>% 
  group_by(newspaper, yearmonth) %>% 
  summarise(size_body_med = median(size_body, na.rm=TRUE)) %>% 
  ggplot(aes(yearmonth, size_body_med, group=newspaper, colour=newspaper)) + 
  geom_line() + 
  labs(x = "month", y = "median number of characters in article") + 
  theme_bw() 
```


```{r}
allnews %>% 
  mutate(size_body = nchar(body), 
         year = date %>% lubridate::floor_date(unit="years")) %>% 
  group_by(newspaper, year) %>% 
  summarise(size_body_med = median(size_body, na.rm=TRUE)) %>% 
  ggplot(aes(year, size_body_med, group=newspaper, colour=newspaper)) + 
  geom_line() + 
  labs(x = "year", y = "median number of characters in article") + 
  theme_bw() 
```


```{r}
allnews %>% 
  mutate(size_body = nchar(body), 
         year = date %>% lubridate::floor_date(unit="years")) %>% 
  group_by(language, newspaper, year) %>% 
  summarise(size_body_med = median(size_body, na.rm=TRUE)) %>% 
  ggplot(aes(year, size_body_med, group=newspaper, colour=newspaper)) + 
  geom_line() + 
  labs(x = "year", y = "median number of characters in article") + 
  theme_bw() + 
  facet_grid(vars(language))
```



```{r}
allnews %>% 
  mutate(size_body = nchar(body)) %>% 
  group_by(newspaper) %>% 
  summarise(size_body_med = median(size_body, na.rm=TRUE)) %>% 
  ggplot(aes(newspaper, size_body_med)) + 
  geom_col() + 
  labs(x = "", y = "median number of characters in article") + 
  theme_bw() 
```


# 2. Presence of "crisis" in the title or the body of text

```{r}
tmp_news <- allnews %>% 
  mutate(
    crisis_title = case_when(
      language %in% c("es","it") ~ title %>% str_to_lower %>% str_detect("crisi"), 
      language %in% c("fr","pt") ~ title %>% str_to_lower %>% str_detect("crise"),  
    ),  
    # crisis_body = case_when(
    #   language %in% c("es","it") ~ body %>% str_to_lower %>% str_detect("crisi"), 
    #   language %in% c("fr","pt") ~ body %>% str_to_lower %>% str_detect("crise"),  
    # ),  
    yearmonth = date %>% lubridate::floor_date(unit="months"),  
    year = date %>% lubridate::floor_date(unit="years")
  )
```



```{r}
tmp_news %>% 
  group_by(newspaper, yearmonth) %>% 
  summarise(crisis_title = mean(crisis_title, na.rm=TRUE)) %>% 
  ggplot(aes(yearmonth, crisis_title, group=newspaper, colour=newspaper)) + 
  geom_line() + 
  labs(x = "month", y = "share of articles with `crisis' in title") + 
  theme_bw() 
```

```{r}
tmp_news %>% 
  group_by(newspaper, year) %>% 
  summarise(crisis_title = mean(crisis_title, na.rm=TRUE)) %>% 
  ggplot(aes(year, crisis_title, group=newspaper, colour=newspaper)) + 
  geom_line() + 
  labs(x = "", y = "share of articles with `crisis' in title") + 
  theme_bw() 
```

```{r}
tmp_news %>% 
  group_by(language,newspaper, year) %>% 
  summarise(crisis_title = mean(crisis_title, na.rm=TRUE)) %>% 
  ggplot(aes(year, crisis_title, group=newspaper, colour=newspaper)) + 
  geom_line() + 
  labs(x = "", y = "share of articles with `crisis' in title") + 
  theme_bw() + 
  facet_grid(vars(language))
```

```{r}
tmp_news %>% 
  group_by(newspaper) %>% 
  summarise(crisis_title = mean(crisis_title, na.rm=TRUE)) %>% 
  ggplot(aes(newspaper, crisis_title)) + 
  geom_col() + 
  labs(x = "", y = "share of articles with `crisis' in title") + 
  theme_bw() 
```


```{r}
# tmp_news %>% 
#   group_by(newspaper, yearmonth) %>% 
#   summarise(crisis_body = mean(crisis_body, na.rm=TRUE)) %>% 
#   ggplot(aes(yearmonth, crisis_body, group=newspaper, colour=newspaper)) + 
#   geom_line() + 
#   labs(x = "month", y = "share of articles with `crisis' in text") + 
#   theme_bw() 
```

```{r}
# tmp_news %>% 
#   group_by(newspaper, year) %>% 
#   summarise(crisis_body = mean(crisis_body, na.rm=TRUE)) %>% 
#   ggplot(aes(year, crisis_body, group=newspaper, colour=newspaper)) + 
#   geom_line() + 
#   labs(x = "", y = "share of articles with `crisis' in text") + 
#   theme_bw() 
```

```{r}
# tmp_news %>% 
#   group_by(language, newspaper, year) %>% 
#   summarise(crisis_body = mean(crisis_body, na.rm=TRUE)) %>% 
#   ggplot(aes(year, crisis_body, group=newspaper, colour=newspaper)) + 
#   geom_line() + 
#   labs(x = "", y = "share of articles with `crisis' in text") + 
#   theme_bw() + 
#   facet_grid(vars(language))
```

```{r}
# tmp_news %>% 
#   group_by(newspaper) %>% 
#   summarise(crisis_body = mean(crisis_body, na.rm=TRUE)) %>% 
#   ggplot(aes(newspaper, crisis_body)) + 
#   geom_col() + 
#   labs(x = "", y = "share of articles with `crisis' in text") + 
#   theme_bw() 
```

# 3. Presence of europ/brexit in the title

```{r}
tmp_news <- allnews %>% 
  mutate(yearmonth = date %>% lubridate::floor_date(unit = "months"), 
         year = date %>% lubridate::floor_date(unit = "years"), 
         europ_title = title %>% str_to_lower %>% str_detect("europ|brexit"))
```


```{r}
tmp_news %>% 
  group_by(yearmonth, newspaper) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(yearmonth, europ_title, group=newspaper, colour=newspaper)) + geom_line() + 
  theme_bw() + 
  labs(x="month",y="share of articles with europ/brexit in title")
```


```{r}
tmp_news %>% 
  group_by(year, newspaper) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(year, europ_title, group=newspaper, colour=newspaper)) + geom_line() + 
  theme_bw() + 
  labs(x="",y="share of articles with europ/brexit in title")
```

```{r}
tmp_news %>% 
  group_by(language, newspaper, year) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(year, europ_title, group=newspaper, colour=newspaper)) + geom_line() + 
  theme_bw() + 
  labs(x="",y="share of articles with europ/brexit in title") + 
  facet_grid(vars(language))
```

```{r}
tmp_news %>% 
  group_by(newspaper) %>% 
  summarise(europ_title = mean(europ_title)) %>% 
  ungroup() %>% 
  ggplot(aes(newspaper, europ_title)) + 
  geom_col() + 
  labs(x = "", y = "share of articles with europ/brexit in title") + 
  theme_bw() 
```


# 4. Presence of references to countries

```{r}
news_countries <- here::here("data","output","news_countries.rds") %>% 
  read_rds()

news_countries %>% count(country) %>% arrange(desc(n))

allnews %>% 
  left_join(news_countries)

allnews %>% 
  inner_join(news_countries, by = "doc_id") %>% 
  count(newspaper, country) %>% 
  arrange(newspaper, desc(n)) %>% 
  group_by(newspaper) %>% slice(1:10)
```

We now have a dataset with, for each article in our data the number of times it mentions each of the countries in the list. 

Question: what summary stats should we produce out of this dataset? 

# 5. Polarity 

## 5.1. Titles 

```{r}
news_polarity <- here::here("data","output","news_polarity_title.rds") %>% 
  read_rds()
```

```{r}
allnews %>% 
  inner_join(news_polarity, by = "doc_id") %>% 
  mutate(yearmonth = date %>% lubridate::floor_date(unit = "months")) %>% 
  group_by(yearmonth, newspaper) %>% 
  summarise(polarity = mean(polarity)) %>% 
  ungroup() %>% 
  ggplot(aes(yearmonth, polarity, group=newspaper, colour=newspaper)) + geom_line() + 
  theme_bw() + 
  labs(x="month",y="average polarity")
```


```{r}
allnews %>% 
  inner_join(news_polarity, by = "doc_id") %>% 
  mutate(year = date %>% lubridate::floor_date(unit = "years")) %>% 
  group_by(year, newspaper) %>% 
  summarise(polarity = mean(polarity)) %>% 
  ungroup() %>% 
  ggplot(aes(year, polarity, group=newspaper, colour=newspaper)) + geom_line() + 
  theme_bw() + 
  labs(x="",y="average polarity")
```

```{r}
allnews %>% 
  inner_join(news_polarity, by = "doc_id") %>% 
  mutate(year = date %>% lubridate::floor_date(unit = "years")) %>% 
  group_by(language, newspaper, year) %>% 
  summarise(polarity = mean(polarity)) %>% 
  ungroup() %>% 
  ggplot(aes(year, polarity, group=newspaper, colour=newspaper)) + geom_line() + 
  theme_bw() + 
  labs(x="",y="average polarity") + 
  facet_grid(vars(language))
```

```{r}
allnews %>% 
  inner_join(news_polarity, by = "doc_id") %>% 
  group_by(newspaper) %>% 
  summarise(polarity = mean(polarity)) %>% 
  ungroup() %>% 
  ggplot(aes(newspaper, polarity)) + 
  geom_col() + 
  labs(x = "", y = "average polarity") + 
  theme_bw() 
```

## 5.2. Body of text

```{r}
news_polarity <- here::here("data","output","news_polarity.rds") %>% 
  read_rds()
```

```{r}
allnews %>% 
  inner_join(news_polarity, by = "doc_id") %>% 
  mutate(yearmonth = date %>% lubridate::floor_date(unit = "months")) %>% 
  group_by(yearmonth, newspaper) %>% 
  summarise(polarity = mean(polarity)) %>% 
  ungroup() %>% 
  ggplot(aes(yearmonth, polarity, group=newspaper, colour=newspaper)) + geom_line() + 
  theme_bw() + 
  labs(x="month",y="average polarity")
```


```{r}
allnews %>% 
  inner_join(news_polarity, by = "doc_id") %>% 
  mutate(year = date %>% lubridate::floor_date(unit = "years")) %>% 
  group_by(year, newspaper) %>% 
  summarise(polarity = mean(polarity)) %>% 
  ungroup() %>% 
  ggplot(aes(year, polarity, group=newspaper, colour=newspaper)) + geom_line() + 
  theme_bw() + 
  labs(x="",y="average polarity")
```

```{r}
allnews %>% 
  inner_join(news_polarity, by = "doc_id") %>% 
  mutate(year = date %>% lubridate::floor_date(unit = "years")) %>% 
  group_by(language, newspaper, year) %>% 
  summarise(polarity = mean(polarity)) %>% 
  ungroup() %>% 
  ggplot(aes(year, polarity, group=newspaper, colour=newspaper)) + geom_line() + 
  theme_bw() + 
  labs(x="",y="average polarity") + 
  facet_grid(vars(language))
```

```{r}
allnews %>% 
  inner_join(news_polarity, by = "doc_id") %>% 
  group_by(newspaper) %>% 
  summarise(polarity = mean(polarity)) %>% 
  ungroup() %>% 
  ggplot(aes(newspaper, polarity)) + 
  geom_col() + 
  labs(x = "", y = "average polarity") + 
  theme_bw() 
```

